Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
mv ml net viz down
render both

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   # bookdown::word_document2:
   #   reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

# Conclusions
Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. We
show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability. Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

>>>>

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

# Conclusion
Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. We
show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability. Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.
